---
title: "week10_assignment_SenapatiKabindra"
output: html_document
---


# 1. Fit a Logistic Regression Model to Thoracic Surgery Binary Dataset

# a. For this problem, you will be working with the thoracic surgery data set 
#install.packages("caTools")
#library("RWeka")
#library("caTools")
```{r}
library("RWeka")
library("caTools")
setwd("/Users/snigdha/Documents/dsc520")
surgerydata <- read.csv("data/ThoraricSurgery.csv",header = TRUE)
```
#b.1. split the data
```{r}

split <- sample.split(surgerydata,SplitRatio = 0.8)
train <- subset(surgerydata, split == "TRUE")
test <- subset(surgerydata, split == "FALSE")
mymodel <- glm(Risk1Yr ~ AGE + PRE4,data=train,family = "binomial")
summary(mymodel)
```
##b.2.According to the summary, which variables had the greatest effect on the survival rate?
#AGE

##b.3To compute the accuracy of your model
```{r}
res <- predict(mymodel,test,type = "response")
res <- predict(mymodel,train,type = "response")
confamatrix <- table(Actual_value = train$Risk1Yr, predicted_value = res > 0.5 )
confamatrix
(confamatrix[[1,1]] )/sum(confamatrix)
```
##2. Fit a Logistic Regression Model

#2.a. Fit a logistic regression model to the binary-classifier-data.csv dataset
```{r}
mydata <- read.csv("data/binary-classifier-data.csv")
mydata$label <- as.factor(mydata$label)
split <- sample.split(mydata,SplitRatio = 0.8)
train <- subset(mydata, split == "TRUE")
test <- subset(mydata, split == "FALSE")

mymodel <- glm(label ~ y ,data=train,family = "binomial")
summary(mymodel)
```
#2.b.The dataset (found in binary-classifier-data.csv) contains three variables; label, x, and y. The label variable is either 0 or 1 and is the output we want to predict using the x and y variables.
```{r}
res <- predict(mymodel,test,type = "response")
res <- predict(mymodel,train,type = "response")

confamatrix <- table(Actual_value = train$label, predicted_value = res > 0.5 )
confamatrix

(confamatrix[[1,1]] + confamatrix[[2,2]])/sum(confamatrix)
```