---
title: "week8_9_Assignment"
output: html_document
---

```{r}
setwd("/Users/snigdha/Documents/dsc520")
##install.packages('xlsx')

library(xlsx)
df_housing  <- read.xlsx("data/week-6-housing.xlsx",sheetName = "Sheet2")
##library(ggplot2)
```


#Create two variables; one that will contain the variables Sale Price and Square Foot of Lot (same variables used from previous assignment on simple regression) and one that will contain Sale Price and several additional predictors of your choice. Explain the basis for your additional predictor selections.
```{r}
sale_lm <-  lm(Sale.Price ~ sq_ft_lot + square_feet_total_living, data = df_housing)

```
#Execute a summary() function on two variables defined in the previous step to compare the model results. What are the R2 and Adjusted R2 statistics?
```{r}
summary(sale_lm)

predicted_df <- data.frame(
  Sale.Price = predict(sale_lm, df_housing), sq_ft_lot = df_housing$sq_ft_lot, square_feet_total_living = df_housing$square_feet_total_living)

mean_price <- mean(df_housing$Sale.Price)
```
```{r}
## Corrected Sum of Squares Total
sst <- sum((mean_price - df_housing$Sale.Price)^2)
## Corrected Sum of Squares for Model
ssm <- sum((mean_price - predicted_df$Sale.Price)^2)
## Residuals
residuals <- df_housing$Sale.Price - predicted_df$Sale.Price
## Sum of Squares for Error
sse <- sum(residuals^2)
## R Squared R^2 = SSM\SST
r_squared <- ssm/sst

#Considering the parameters of the multiple regression model you have created. What are the standardized betas for each parameter and what do the values indicate?
n <- 1192
## Number of regression parameters
p <- 2
## Corrected Degrees of Freedom for Model (p-1)
dfm <- p-1
## Degrees of Freedom for Error (n-p)
dfe <- n-p
## Corrected Degrees of Freedom Total:   DFT = n - 1
dft <- n -1

## Mean of Squares for Model:   MSM = SSM / DFM
msm <- ssm/dfm
## Mean of Squares for Error:   MSE = SSE / DFE
mse <- sse/dfe
## Mean of Squares Total:   MST = SST / DFT
mst <- sst/dft
## F Statistic F = MSM/MSE
f_score <- msm/mse

## Adjusted R Squared R2 = 1 - (1 - R2)(n - 1) / (n - p)
adjusted_r_squared <- 1 - (1 - r_squared)*(n - 1) / (n - p)

## Calculate the p-value from the F distribution
p_value <- pf(f_score, dfm, dft, lower.tail=F)

```